SUPPLEMENTARY INFORMATION: Overlay databank unlocks data-driven analyses of biomolecules for all

### 2023-10-21 SI.tex
Updates from Overleaf
Update text

\pagebreak
\section{Testing machine learning models against literature data}
\begin{figure}[hb]
    \centering
    \includegraphics[width=50mm]{Figures/MLtest/Ridgetest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/Lassotest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/ElasticNettest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/DecisionTreeRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/RandomForestRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/GradientBoostingRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/AdaBoostRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/KNeighborsRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/MLPRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/XGBRegressortest.pdf}
    \caption{Predictions of area per lipids of POPC, POPE, POPS, PI, sphingomyelin lipids and cholesterol from the tested machine learning models against literature data from simulations
      (green~\cite{shahane19}, blue~\cite{kumar21}, and red~\cite{oliveira22}). The black line depicts x=y where the prediction equals the litterature value.}
    \label{fig:MLTest}
\end{figure}

>>>>

\pagebreak
\section{Testing machine learning models against literature data}
\begin{figure}[hb]
    \centering
    \includegraphics[width=50mm]{Figures/MLtest/LinearRegressiontest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/Ridgetest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/MLPRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/Lassotest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/ElasticNettest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/DecisionTreeRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/RandomForestRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/GradientBoostingRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/AdaBoostRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/KNeighborsRegressortest.pdf}
    \includegraphics[width=50mm]{Figures/MLtest/XGBRegressortest.pdf}
    \caption{Predictions of area per lipids of multi-component membranes composed of POPC, POPE, POPS, PI, sphingomyelin lipids and cholesterol from linear regression model against literature data from simulations 
      (green~\cite{shahane19}, blue~\cite{kumar21}, and red~\cite{oliveira22}). Mean squared error (RMSE) and Pearson correlation coefficient are shown for each model. The black line depicts x=y where the prediction equals the literature value.}
    \label{fig:MLTest}
\end{figure}
